A Data-Driven Framework for Neural Field Modelling

### 2010-11-17 ltx/first_order_framework/LaTeX_Manuscript.tex
added a couple of notes

% The size of the squares in the figure show the magnitude of the log of the error. The squares are black if the log of the error is negative (the RMSE is $<1$) and the squares are white if the log of the error is positive (the RMSE is $>1$). The largest black squares indicate the best performance and the largest white squares indicate the worst performance for the parameter combinations (\dean{need some thing more quantitative}). 
From Figure~\ref{fig:Figure12} it can be seen that the estimation accuracy depends on the parameters of the sigmoid function. This is expected since that by altering the parameters we are changing the nonlinearity and the saturation region of the sigmoid.

..\dean{This next bit is CRAP (please help):} When the threshold is negative or the slope is very gentle, all of the activity is being passed through the sigmoid function. However, as the slope is increased or the threshold is increased, more of the field is within the saturating region of the activation function. This is illustrated in Figure~\ref{fig:sigmoidfunctions}, where the sigmoids from the bottom left corner through to near top right corner of Figure~\ref{fig:sigmoidfunctions} are plotted. This appears to have a detrimental effect on the estimation accuracy.

@@

\section{Conclusion}
This paper has made a contribution to bridging the gap between experimental and theoretical neuroscience by developing a systematic methodology. \dean{Please add to this.} Novel aspects of this work include a model reduction procedure such that a finite-dimension state-space model constructed...

>>>>

% The size of the squares in the figure show the magnitude of the log of the error. The squares are black if the log of the error is negative (the RMSE is $<1$) and the squares are white if the log of the error is positive (the RMSE is $>1$). The largest black squares indicate the best performance and the largest white squares indicate the worst performance for the parameter combinations (\dean{need some thing more quantitative}). 
From Figure~\ref{fig:Figure12} it can be seen that the estimation accuracy depends on the parameters of the sigmoid function. This is expected since that by altering the parameters we are changing the nonlinearity and the saturation region of the sigmoid.  
\dean{PLEASE HELP TO FILL THIS SECTION IN. ANYTHING WILL DO.}
..\dean{This next bit is CRAP (please help):} When the threshold is negative or the slope is very gentle, all of the activity is being passed through the sigmoid function. However, as the slope is increased or the threshold is increased, more of the field is within the saturating region of the activation function. This is illustrated in Figure~\ref{fig:sigmoidfunctions}, where the sigmoids from the bottom left corner through to near top right corner of Figure~\ref{fig:sigmoidfunctions} are plotted. This appears to have a detrimental effect on the estimation accuracy.

@@

\section{Conclusion}
This paper has made a contribution to bridging the gap between experimental and theoretical neuroscience by developing a systematic methodology. \dean{Please add to this.} Novel aspects of this work include a model reduction procedure such that a finite-dimension state-space model constructed... \dean{PLEASE HELP TO FILL THIS SECTION IN. ANYTHING WILL DO.}
